### 2016-03-25 paper.tex
Update game name
Update paper title

\newcommand{\projecttitle}{The Culture-Narration Genre: Defining the genre and identifying its potential for educational games}

@@

\begin{figure}
\newcommand{\colwidth}{0.48\columnwidth}
% http://tex.stackexchange.com/questions/2441/how-to-add-a-forced-line-break-inside-a-table-cell
\newcommand{\specialcell}[2][t]{%
  \begin{tabular}[#1]{@{}p{\colwidth}@{}}#2\end{tabular}}
\centering
\begin{tabular}{|p{\colwidth}|p{\colwidth}|}\hline
\specialcell{
\\
\totan{} encounter \#1965\\
\\
Many seaside villages have reported sightings and attacks from
a large pirate fleet. There are far too many ships in the fleet to attack
on your own, so you need to find a powerful prince who can stand up to
the pirate captains.\\
\\
\textit{Use Storytelling Skill}\\
\\
You present the plight of the villagers with such eloquence and
style that every prince you address promises to aid in the
defeat of these rampaging pirates. When you see the size of the
fleet sent to destroy the renegades, you have no doubt in the eventual
triumph of justice. [Gain 1 Destiny Point and Courtly Graces skill.]
}
&
\specialcell{
\\
\smersh{} encounter \#20.4.1\\
\\
You have uncovered evidence that UN Agent F9 also works for the CIA.
You're not convinced that's necessarily a bad thing, but the Director
is taking it very seriously. You must find out if he is a threat.\\
\\
You meet with F9 and act as if everything is perfectly normal, exchanging
information about a case you are working together. When he leaves, you follow
him in your Ferrari.\\
\\
\textit{Successfully pass Spycraft test using Driving skill}\\
\\
He is highly experienced at spotting tails, but you are equally experienced
in avoiding being spotted. You follow him to a hotel where he meets
with a Soviet diplomat. Never mind the CIA: it seems he's working for the
KGB. [Improve any two skills.]
}
\\\hline
\specialcell{
\\
\textit{Above and Below} encounter \#62\\
\\
You follow a square tunnel, the walls smooth and masterfully cut.
Before long you reach a tall chamber; in the center sits a great crystal,
floating in mid-air. A dim, violet glow emanates from it and as you approach
a voice fills the air. ``I am the crystal of oracles. If you can prove
your worth, I will give you knowledge.'' Do you continue speaking to the
crystal or explore some of the connecting passages?\\
\\
\textit{Explore the passages}:\\
3 successes: gain two coins\\
5 successes: gain a coin, a fish, and a mushroom
}
& 
\specialcell{
\\
\textit{Monster Journal} encounter\\
\\
As you're sitting on the edge of a river, you see a large turtle swimming towards you. When it gets close it launches from the water to reveal it's not a turtle, but a kappa!\\
\\
\textit{Use Logic skill}\\
\\
Remembering Japanese manners, you give the kappa a greeting bow. It returns your bow, emptying the water-filled dip on its head. It loses its strength and crawls to the water. [Gain 1 Inspiration]
}
\\\hline
\end{tabular}
\caption{Sample encounters}
\label{fig:encounters}
\end{figure}

@@

The title and theme of our game changed between iterations as we came
to better understanding of the interplay between genre, rules, and our
players.  The final version---\textit{Monster Journal}---positioned
two players as rival authors seeking inspiration from monsters around
the world. The players travel across Africa, Asia, Europe, Oceania,
and North and South America to encounter monsters from local folklore.
Encounters are patterned after \totan{} as illustrated in
Figure~\ref{fig:encounters}, and the game exhibits the five characteristics
identified for cultural-narration games.

>>>>

\newcommand{\projecttitle}{Culture-narration games: a definition and pilot study}

@@

\begin{figure}
\newcommand{\colwidth}{0.48\columnwidth}
% http://tex.stackexchange.com/questions/2441/how-to-add-a-forced-line-break-inside-a-table-cell
\newcommand{\specialcell}[2][t]{%
  \begin{tabular}[#1]{@{}p{\colwidth}@{}}#2\end{tabular}}
\centering
\begin{tabular}{|p{\colwidth}|p{\colwidth}|}\hline
\specialcell{
\\
\totan{} encounter \#1965\\
\\
Many seaside villages have reported sightings and attacks from
a large pirate fleet. There are far too many ships in the fleet to attack
on your own, so you need to find a powerful prince who can stand up to
the pirate captains.\\
\\
\textit{Use Storytelling Skill}\\
\\
You present the plight of the villagers with such eloquence and
style that every prince you address promises to aid in the
defeat of these rampaging pirates. When you see the size of the
fleet sent to destroy the renegades, you have no doubt in the eventual
triumph of justice. [Gain 1 Destiny Point and Courtly Graces skill.]
}
&
\specialcell{
\\
\smersh{} encounter \#20.4.1\\
\\
You have uncovered evidence that UN Agent F9 also works for the CIA.
You're not convinced that's necessarily a bad thing, but the Director
is taking it very seriously. You must find out if he is a threat.\\
\\
You meet with F9 and act as if everything is perfectly normal, exchanging
information about a case you are working together. When he leaves, you follow
him in your Ferrari.\\
\\
\textit{Successfully pass Spycraft test using Driving skill}\\
\\
He is highly experienced at spotting tails, but you are equally experienced
in avoiding being spotted. You follow him to a hotel where he meets
with a Soviet diplomat. Never mind the CIA: it seems he's working for the
KGB. [Improve any two skills.]
}
\\\hline
\specialcell{
\\
\textit{Above and Below} encounter \#62\\
\\
You follow a square tunnel, the walls smooth and masterfully cut.
Before long you reach a tall chamber; in the center sits a great crystal,
floating in mid-air. A dim, violet glow emanates from it and as you approach
a voice fills the air. ``I am the crystal of oracles. If you can prove
your worth, I will give you knowledge.'' Do you continue speaking to the
crystal or explore some of the connecting passages?\\
\\
\textit{Explore the passages}:\\
3 successes: gain two coins\\
5 successes: gain a coin, a fish, and a mushroom
}
& 
\specialcell{
\\
\textit{Traveler's Notebook} encounter\\
\\
As you're sitting on the edge of a river, you see a large turtle swimming towards you. When it gets close it launches from the water to reveal it's not a turtle, but a kappa!\\
\\
\textit{Use Logic skill}\\
\\
Remembering Japanese manners, you give the kappa a greeting bow. It returns your bow, emptying the water-filled dip on its head. It loses its strength and crawls to the water. [Gain 1 Inspiration]
}
\\\hline
\end{tabular}
\caption{Sample encounters}
\label{fig:encounters}
\end{figure}

@@

The title and theme of our game changed between iterations as we came
to better understanding of the interplay between genre, rules, and our
players.  The final version---\textit{Traveler's Story: Monster
  Tales}---positioned two players as rival authors seeking inspiration
from monsters around the world. The players travel across Africa,
Asia, Europe, Oceania, and North and South America to encounter
monsters from local folklore.  Encounters are patterned after \totan{}
as illustrated in Figure~\ref{fig:encounters}, and the game exhibits
the five characteristics identified for cultural-narration games.
